\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
better/clearer wording

There are some important issues which must be considered to perform an accurate conversion. 
A Geant4 logical volume solid might need to be created from a FLUKA region composing of many zones, 
so $R_1 = +z_1\: | +z_2$, similarly a void is required to locate daughter volume placements which again 
might also be converted to a region of multiple zones $R_2= +z_3 \: | +z_4$. So creating the FLUKA region is then 
\begin{eqnarray}
R_1 - R_2 	& = & (+z_1 \: | +z_2) - ( +z_3 \: | +z_4) 			\\
			& = & (+z_1 - z_3 - z_4) \;  | \; (+z_2 - z_3 - z_4)	
\label{eqn:setDiff}
\end{eqnarray}
Geant4 has the Boolean solids associated with difference, union and intersection, so in addition to 
Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and $R_1 \cap R_2$ is required in FLUKA notation, so 
\begin{eqnarray}
R_1 \cup R_2 	& = & (+z_1 \: | +z_2)  \cup ( +z_3 \: | +z_4) \\
			& = & +z_1 \: | +z_2 |  +z_3 \: | +z_4
\label{eqn:setUnion}
\end{eqnarray}
and 
\begin{eqnarray}
R_1 \cap R_2 	& = & (+z_1 \: | +z_2) \cap ( +z_3 \: | +z_4) \\
			& = & +z_1 +z_3  \; | +z_1 +z_4 \; | +z_2 +z_3 \; | +z_2 +z_4
\label{eqn:setIntersection}
\end{eqnarray}

>>>>

There are some important issues which must be considered to perform an accurate conversion. 
A Geant4 logical volume solid might need to be created from a FLUKA region consisting of many zones (i.e. unions), 
so $R_1 = +z_1\: | +z_2$, similarly a void is required to locate daughter volume placements which again 
might also be converted to a region of multiple zones $R_2= +z_3 \: | +z_4$. So creating the FLUKA region is then 
\begin{eqnarray}
R_1 - R_2 	& = & (+z_1 \: | +z_2) - ( +z_3 \: | +z_4) 			\\
			& = & (+z_1 - z_3 - z_4) \;  | \; (+z_2 - z_3 - z_4)	
\label{eqn:setDiff}
\end{eqnarray}
Geant4 has the Boolean solids associated with difference, union and intersection, so in addition to 
Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and $R_1 \cap R_2$ is required in FLUKA notation, so 
\begin{eqnarray}
R_1 \cup R_2 	& = & (+z_1 \: | +z_2)  \cup ( +z_3 \: | +z_4) \\
			& = & +z_1 \: | +z_2 |  +z_3 \: | +z_4
\label{eqn:setUnion}
\end{eqnarray}
and 
\begin{eqnarray}
R_1 \cap R_2 	& = & (+z_1 \: | +z_2) \cap ( +z_3 \: | +z_4) \\
			& = & +z_1 +z_3  \; | +z_1 +z_4 \; | +z_2 +z_3 \; | +z_2 +z_4
\label{eqn:setIntersection}
\end{eqnarray}
